\documentclass[twocolumn,8pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{mdframed}
\usepackage[svgnames,dvipsnames,usenames]{xcolor}
\usepackage{listings}
\usepackage[ampersand]{easylist}
\usepackage{textcomp}
\usepackage[top=0.35cm,left=0.35cm,right=0.35cm,bottom=0.35cm]{geometry}
\usepackage{soul}
\usepackage[shortlabels]{enumitem}

\lstset{
    language=bash,
    frame=single,
    backgroundcolor=\color{white},
    basicstyle=\small,
    showspaces=false
}

\setlength{\parindent}{0pt}

\title{CMCC - Monitoring}
\author{Fabio Viola}
\date{March 2020}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}


\LARGE \textbf{Monitoring GOFS quick ref.}  \hfill \textit{\small Fabio Viola}\normalsize

% NIGHT
\mdfsetup{
    roundcorner = 5pt,
    frametitlerule=true,
    frametitlebackgroundcolor=MidnightBlue!70,
    frametitlefont={\bfseries\color{white}},
    backgroundcolor=MidnightBlue!15!white,
    linecolor=MidnightBlue!70,
    linewidth=1pt,
    innerbottommargin=3pt,
    innertopmargin=3pt,
    skipbelow=0pt,
}

\begin{mdframed}[frametitle=(A.0)\ -- At 8 pm\hfill\faMoonO]

Check (\faEnvelope) that input data is available through the emails:
\begin{itemize}\itemsep0pt
    \item \texttt{[eni\_oce] [\textit{YYYYMMDD}-Zeus]: NCEP original data available for GOFS production}
    \item \texttt{[eni\_oce] [\textit{YYYYMMDD}]: NOAA original data available for GOFS production} (around 6.30 pm daylight saving time or 7.pm solar time). 
    \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Message present! -- the workflow can start\dots
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Message missing!}} -- \textit{a bakcup procedure will start. We will receive around 8 pm an email with subject:} "\texttt{[eni\_oce] [\textit{YYYYMMDD}]: NOAA backup data available}" \textit{(date of yesteday).}
    \end{itemize}
\end{itemize}
\end{mdframed}

\begin{mdframed}[frametitle=(A.1)\ -- At 8.30 pm\hfill\faMoonO]

Check (\faEnvelope) that production is started through the email with topic: "\texttt{[ZEUS-GOFS-OP][\textit{YYYYMMDD}]}" or (\faSend) with the message "\texttt{GOFS-ZEUS production cycle for \textit{YYYYMMDD} is going to start ...}".
    \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Message/email present! -- the workflow has started!\dots
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Message/email missing!}} -- Production hasn't started! \hl{What to do?}
    \end{itemize}
\end{mdframed}

\begin{mdframed}[frametitle=(A.2)\ -- At 10 pm\hfill\faMoonO]

Check (\faSend) that production is proceeding with:
"\textit{ZEUS-NEMO run for \textit{YYYYMMDD} has been completed in \textit{X} secs}". Email (\faEnvelope) with topic "\texttt{[ZEUS-GOFS-OP][\textit{YYYYMMDD}]NEMO Completed}" should also arrive.
    \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Message/email present! -- Let's go out to celebrate!
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Message/email missing!}} -- Problems! \hl{What to do?}
    \end{itemize}
\end{mdframed}

%% DAY
\mdfsetup{
    frametitlerule=true,
    frametitlebackgroundcolor=Cerulean,
    frametitlefont={\bfseries\color{white}},
    backgroundcolor=Cerulean!15!white,
    linecolor=Cerulean!90!white,
    linewidth=1pt,
    innerbottommargin=3pt,
    innertopmargin=3pt,
    skipbelow=0pt,
}

\begin{mdframed}[frametitle=(B.0)\ -- At 9 am\hfill\faSunO]

Check (\faSend) that we received message: "\texttt{\textit{YYYYMMDD} - ZEUS Ocean prod\-ucts successfully produced and ready for the upload to ENI ftp}"
    \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Message present! -- Go on with the next step\dots
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Message missing!}} -- probably Athena is down!
    \end{itemize}

\faInfoCircle\ \textit{This check is for hourly data, files that \ul{must} be sent to ENI. These files can be found on Zeus, under the path} \texttt{/work/opa/gofs/products/GlobEni}.

\end{mdframed}

\begin{mdframed}[frametitle=(B.1)\ -- At 9 am\hfill\faSunO]

Check (\faEnvelope) that:

\begin{enumerate}\itemsep0pt
    \item we received the email with topic "\texttt{[ZEUS GOFS-OP][\textit{YYYYMMDD}]}" that communicates the end of the production;
    \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Email present! -- We can go on with the next step\dots
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Email missing!}} -- probably Athena is down!
    \end{itemize}
    \item the size of data produced is coherent with the expected size (both are reported in the email).
    \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Sizes are coherent with the expectations.
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Sizes are incoherent.}} \hl{What to do?}
    \end{itemize}
\end{enumerate}

\faInfoCircle\ \textit{This check is for daily data, less critical than B.0.}

\end{mdframed}    

\begin{mdframed}[frametitle=(B.2)\ -- At 9 am\hfill\faSunO]

Check (\faEnvelope) that:

\begin{enumerate}\itemsep0pt
    \item we received an email for each of the file produced. Topic of these emails should be "\texttt{[ZEUS-GOFS-OP][\textit{YYYYMMDD}]NEMO Completed}";
        \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] 8 emails are present!
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{At least an email is missing!}} \hl{What to do?}
        \end{itemize}
    \item in each message check that the elapsed time is $\approx$ 1600 s.
        \begin{itemize}\itemsep0pt
        \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Every time interval is close to 1600 s.
        \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{At least one is noticeably smaller/higher!}} \hl{What to do?}
        \end{itemize}
\end{enumerate}
\end{mdframed}    


\begin{mdframed}[frametitle=(C)\ -- At 9 am\hfill\faSunO]

Fill the \href{https://docs.google.com/spreadsheets/d/1XrbzNdr-K6jtwD-tTdRAlaO6S9hy3aSgxQ-OCmYEfL0/edit#gid=1550543264}{\textbf{Google Drive \faExternalLink}}\ row of the current day, reporting:
\vspace{-5pt}
\begin{enumerate}[col.\ A:\ , left=0.25cm, start=3,align=parleft]\itemsep0pt
    \item Who is carrying out the monitoring operations.
    \item If the production ended successfully (\faCheck) or not (\faTimes).
    \item Comments about issues (if any).
    \item Causes of the issues (if known).
    \addtocounter{enumi}{1}
    \item Start/end of regional files.
    \item Clean of regional files.
    \item Comments on regional data.
    \item General comments.
\end{enumerate}

\textbf{Note 1:} if we used NOAA backup data (see box A.0), report "NOAA Backup" in column E.

\

\textbf{Note 2:} report WRF Backup in column E if we invoked the backup procedure. Adding comments in column F would be great.

\end{mdframed} 

\begin{mdframed}[frametitle=(D)\ -- Before 11.30 am\hfill\faSunO]

Disable upload if files are missing:
\vspace{-5pt}
\begin{itemize}\itemsep0pt
    \item Connect to zeus and open crontab:
\begin{lstlisting}
$ ssh gofs@zeus01.cmcc.scc
$ EDITOR=nano crontab -e
    \end{lstlisting}
    
    \item Comment the following line:
    \begin{lstlisting}
30 11 * * * /users_home/opa/gofs/gofs_op/..
    \end{lstlisting}
\end{itemize}

\textbf{NOTE:} please remember to uncomment it after 11.30!

\end{mdframed} 


\begin{mdframed}[frametitle=(E)\ -- Around 11.50 am\hfill\faSunO]

Check (\faSend) if upload ended successfully. If we received a Telegram message with: "\texttt{PD=YYYYMMDD - ENI-OCEAN PRODS PROCESS EXECUTED.}", everything is allright.

\begin{itemize}\itemsep0pt
    \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Received -- Put \faCheck\ in col.\ G of the \href{https://docs.google.com/spreadsheets/d/1XrbzNdr-K6jtwD-tTdRAlaO6S9hy3aSgxQ-OCmYEfL0/edit#gid=1550543264}{\textbf{Google Drive \faExternalLink}} doc. 
    
    \item[{\textcolor{Red}{\faTimesCircle}}] \ul{\textbf{Not received}} -- Put \faTimes\ in col.\ G of the \href{https://docs.google.com/spreadsheets/d/1XrbzNdr-K6jtwD-tTdRAlaO6S9hy3aSgxQ-OCmYEfL0/edit#gid=1550543264}{\textbf{Google Drive \faExternalLink}} document. 
\end{itemize}

\end{mdframed} 

% \vfill

% \begin{mdframed}[frametitle=Final remarks]
% \begin{itemize}\itemsep0pt
%     \item Telegram messages contains more information than emails. Nonetheless, these systems are complementary to each other.
    
%     \item Important information about errors can be found on Zeus, under \texttt{/work/opa/gofs/gofs\_working/logs/YYYYMMDD/}
    
%     \item Outcome of the elaboration is in \texttt{/data/products/GOFS}. Folder \texttt{globEni\_Zeus} contains data that should be transferred to ENI. \texttt{globNative\_Zeus} contains daily data written by NEMO. \texttt{globWeb} contains file related to the rebuild of hourly data.
    
%     \item More information is available in the  \href{https://docs.google.com/presentation/d/1GtyfHDRA8M8fqbOj-mrj2zuq521KK_PiMLw-3JQ7jYQ/edit?usp=sharing}{\textbf{GOFS16 Simplified Manual \faExternalLink}}
% \end{itemize}
% \end{mdframed} 

{\hfill\footnotesize\textbf{Last update:} \today}

\end{document}
