\documentclass[twocolumn,8pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{mdframed}
\usepackage[svgnames,dvipsnames,usenames]{xcolor}
\usepackage{listings}
\usepackage[ampersand]{easylist}
\usepackage{textcomp}
\usepackage[top=0.5cm,left=0.5cm,right=0.5cm,bottom=0.5cm]{geometry}
\usepackage{soul}

\lstset{
    language=bash,
    frame=single,
    backgroundcolor=\color{white},
    basicstyle=\small,
    showspaces=false
}

\setlength{\parindent}{0pt}

\title{CMCC - Monitoring}
\author{Fabio Viola}
\date{March 2020}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\mdfsetup{
    roundcorner = 5pt,
    frametitlerule=true,
    frametitlebackgroundcolor=YellowOrange,
    frametitlefont={\bfseries\color{white}},
    backgroundcolor=YellowOrange!15!white,
    linecolor=YellowOrange!90!white,
    linewidth=1pt,
    innerbottommargin=6pt,
    innertopmargin=6pt,
    skipbelow=3pt,
}

\LARGE \textbf{Monitoring WRF quick ref.}  \hfill \textit{\small Fabio Viola}\normalsize

\begin{mdframed}[frametitle=(A)\ -- Before 8.45 am]

On telegram "WRF Messages" we can receive one of the following messages (\texttt{\$DP}: production date as \texttt{YYYYMMDD}):
\begin{itemize}\itemsep0pt
\item[{\textcolor{ForestGreen}{\faCheckCircle}}] Il 16\textdegree\, dei venti di oggi (\texttt{\$DP}) è andato!
\item[{\textcolor{Red}{\faTimesCircle}}] Il 16\textdegree\, dei venti di oggi (\texttt{\$DP}) ci ha lasciati! La cosa è grave
\end{itemize}
\ul{In case of error} see \textbf{Recover A}.

\end{mdframed}    

\begin{mdframed}[frametitle=(Recover A)\ -- Before 10 am]
\begin{enumerate}\itemsep0pt
    \item Open \href{http://athena01.cmcc.scc:58082/static/visualiser/index.html#}{\textbf{Luigi\ \faExternalLink}} and check the process \texttt{WindToENI}, to get information from the red bullets.
    
    \item Connect to Athena:
    \begin{lstlisting}
$ ssh gofs@athena01.cmcc.scc
    \end{lstlisting}
    
    \item Check that files \texttt{\$\{area\}\_1.16\_XXX.grib} are present:
    \begin{lstlisting}[breaklines=true, showspaces=false, showstringspaces=false, language=bash]
$ area="Angola Arctic Australia Britain Caribbean Caspian.Sea China.Sea Guinea Gulf.Mex Med.Central Med.East Med.West Mozambique Red.Sea OMANXX" 
$ for i in ${area}; do echo ${i}; ls /work/tessa_gpfs2/wrf/output/${i}_1.16_*.grib | wc -l; done
    \end{lstlisting}
\end{enumerate}

Two options:
\begin{itemize}\itemsep0pt
    \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Files are 157 for every region
    \item[{\textcolor{Red}{\faTimesCircle}}] One or more regions have less than 157 files
\end{itemize}

\ul{In case of error} see \textbf{Recover B} and \textbf{Recover C}.

\end{mdframed}


\begin{mdframed}[frametitle=(Recover B)\ -- Before 10 am]

Check which regions are incomplete:

\begin{itemize}\itemsep0pt
    \item If \textbf{Red sea} or \textbf{Arctic}: since this data is produced by the Greeks, we can immediately send the email (see below)
    \item Else, the problem is on our side. \ul{Before} sending the email, check that the problem is not due to available space! Check with \texttt{df -h} on \texttt{das@okeanos.cmcc.scc}. At least 3.5 TB should be available. Otherwise, \textbf{we don't send the email}.
\end{itemize}

%Write an \href{mailto:chrisstath@mg.uoa.gr}{email to Christos\ \faEnvelope}:
Write an \href{mailto:eni_atm@cmcc.it}{email to ENI\_ATM\ \faEnvelope}:


\begin{quote}
\textbf{Oggetto: }[eni\_atm] [WRF] lack of some outputs\\
\textbf{Testo:}\\
Dear all, \\
this mail is to inform you that into the folder of WRF today's production (/work/tessa\_gpfs2/wrf/output/) there were some missing outputs:

--\ \textit{list of missing outputs}

Could you please check the encountered issues and provide a description of them for internal tracking purposes?


Thanks a lot.

Best Regards
\end{quote}
\end{mdframed}
 
\begin{mdframed}[frametitle=(Recover C)\ -- Before 11 am]

When files are missing, we have to provide our backup data. So:

\begin{enumerate}\itemsep0pt
    \item Open \href{http://athena01.cmcc.scc:58082/static/visualiser/index.html#}{\textbf{Luigi\ \faExternalLink}} and go to \textbf{Workers}, then kill the process \texttt{SubmitWindToEni} (generally shown at the end of the page)
    
    \item Connect to Athena and kill job \texttt{EniWnd16}:
    \begin{lstlisting}
$ ssh gofs@athena01.cmcc.scc
$ bkill -J EniWnd16
    \end{lstlisting}
    
    \item Check that backup files are present (\texttt{DP} is set to yesterday):
    \begin{lstlisting}[breaklines=true,showstringspaces=false]
$ DP=YYYYMMDD
$ area="Angola Arctic Australia Britain Caribbean Caspian.Sea South.China Guinea Gulf.Mex Med.Central Med.East Med.West Mozambique Red.Sea OMANXX"
$ for i in ${area}; do echo ${i}; ls  /work/tessa_gpfs2/archive/rolling/raw/atmos/NCEP/GFS025/1.0forecast/6h/${DP}/backup/${i}_1.16_*.grib | wc -l; done
    \end{lstlisting}
\end{enumerate}

After the last command, we have two options:
\begin{itemize}\itemsep0pt
    \item[{\textcolor{ForestGreen}{\faCheckCircle}}] Files are 121 for every region
    \item[{\textcolor{Red}{\faTimesCircle}}] One or more regions have less than 121 files
\end{itemize}

If \ul{no error occurred}, then:
\begin{lstlisting}
$ cd /users/home/gofs/wrf
$ nohup runEniWindBKP.sh &
\end{lstlisting}

\ul{In case of error} see \textbf{Recover D}.

\end{mdframed}

\begin{mdframed}[frametitle=(Recover D)\ -- Before 11 am]

If backup files are also missing:

\begin{enumerate}\itemsep0pt
    \item Connect to zeus:
    \begin{lstlisting}
$ ssh das@okeanos.cmcc.scc
    \end{lstlisting}
    
    \item Run:
\begin{lstlisting}[breaklines=true]
$ sh /users/home/tessa_gpfs1/das/NCEP/post-proc/script/copy/process_ENI_good.sh
\end{lstlisting}

\end{enumerate}

then, go back to \textbf{Recover C, point 3}.

\end{mdframed}

\begin{mdframed}[frametitle=(E)\ -- Before 11.30 am]

Disable upload if files are missing:

\begin{itemize}\itemsep0pt
    \item Connect to zeus and open crontab:
\begin{lstlisting}
$ ssh gofs@zeus01.cmcc.scc
$ EDITOR=nano crontab -e
    \end{lstlisting}
    
    \item Comment the following line:
    \begin{lstlisting}
30 11 * * * /users_home/opa/gofs/gofs_op/..
    \end{lstlisting}
\end{itemize}

\textbf{NOTE:} please remember to uncomment it after 11.30!

\end{mdframed}


{\hfill\footnotesize\textbf{Last update:} \today}

\end{document}
